Information Closure Theory of Consciousness

### 2019-09-11 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

        The two examples show that coding schemes through coarse-graining can provides a stochastic system, e.g. the neural system, more stable and deterministic macroscopic processes to encode and process information reliably. We argue that through coarse-graining the neural systems is able to form NTIC processes at macroscopic levels. Based on this argument, we proposes our theory of consciousness in the next section.

@@

        % ---------------------------------------------------------------------------- %
        %                            Unconscious Processing                            %
        % ---------------------------------------------------------------------------- %
        \subsection{Unconscious Processing}
        \ac{OurTheory} proposes that NTIC is sufficient for a process to be conscious. Here, we highlights three scenarios that

        First, a process is not informational closed leads to low NTIC (Eq.~\ref{eq:nticObjective2}, and, therefore, low conscious levels or no consciousness. In this case, the current states of the process are largely determined by its environment.

        We highlight two scenarios that a process is functional, however, but unconscious.

        \subsubsection*{Fail to meet the 1\lowercase{st} condition}
            If a process fails to fulfil either of the two conditions, information remains unconscious. We first consider the scenario that a process fails to satisfy the first condition, i.e. the process fails to form high degree of NTIC. In the neural system many processes fall into this category.

        	Considering the objectives of achieving NTIC (Eq. \ref{eq:nticObjective}), if a process is unable to maximise the mutual information between its past and future states ($I(Y_{t+1};Y_{t})$), it results in low NTIC. The failure to maximise the mutual information implies the past states of the process itself has little influence on its future states. In the meantime, if environmental information is able to flow into the process, the process can still produces functional outputs based on the current state of the environment accordingly. However, in this circumstance, the future state of the process is largely determined by the environmental states. That is, the process is not informationally closed (${J_{t}(E \rightarrow Y )} \not\approx 0$, Fig.~\ref{fig:reflexive}).

            % or minimise $I(Y_{t+1};Y_{t}|E_{t})$

            % If the future states of the system have strong mutual information with the current environmental states ($I(Y_{t+1};E_{t})$) but have weak mutual information with the current system states ($I(Y_{t+1};Y_{t})$), the informational closeness will be small.

        	% reflexive behaviour
    		\begin{figure}[H]
    			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
    			\caption{Reflexive Behaviours}
    			\label{fig:reflexive}
    		\end{figure}

            In the neural system, this type of processes, for perception, shows the property that the perceptual processing mainly passively responds to the sensory inputs. For actions, this type of processes only produces "reflective-like" behaviours. Reflexive behaviours are commonly considered as automatic and non-conscious behavioural controls \citep{casali2013theoretically}\needref{More referene}. We argue that information carried by this type of processes is unconscious due to its failure of achieving high NTIC, i.e., the first condition.

            The same principle can be applied to blindsight and procedure memory \needref{blindsight} which are often considered as unconscious processing. Blindsight patients are able to track objects, avoid obstacles, and make above chance-level judgements without having any conscious perception about visual stimuli. We believe that these behaviours can be guided by direct stimulus-response mappings ($S\rightarrow{}R$). However, the direct $S\rightarrow{}R$ mappings also lead to non-NTIC neural processes  and, therefore, are unconscious. Similarly, in the case of procedure memory, processes always rely on both the current environmental and system states to determine the next state of the processes\needref{Do I need ref??}. The information flow from the environment to the system is crucial to guide the state transition of procedural memory. Therefore, information processing of procedural memory also fails to form high NTIC and remain unconscious.

             This type of processing is similar to the model-free policy-based agents in the reinforcement learning framework. The agent learns a policy $\pi$ which directly maps sensor values $S$ to output action $A$.
    		\begin{equation}
    			\label{eq:PolicyBasedAgent}
    			\begin{aligned}
    			    \pi(A | S)=\operatorname{Pr}\left(A_{t}=a | S_{t}=s\right)
    			\end{aligned}
    		\end{equation}

    		Our theory can explain why the patients with visual apperceptive agnosia (e.g., the famous case D.F.\cite{james2003ventral}) can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}. The online visual information can be used to perform functional actions without forming an NTIC process. Our theory also explains why unconscious processes in this category often fail when a long delay periods is introduced in the tasks. Without self-predictive information in NTIC, the policies of motor outputs largely depends on the present environmental and sensory states implying that this type of processes often can only work online. With a long, sensory information is unable to guide the delayed motor outputs and leads to failure consequences.

    		Finally, an interesting implication from our theory is that a pure feedforward neural network cannot be conscious because it is unable to maintain any form of memory so that there is no influence from the system past states to its future state. In contrast, with recurrent loops, a neural network is able to create information channels from its past to its future states and becomes capable of achieving NTIC. This result coincides with some theories of consciousness which emphasize the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
    		% if more references are needed, check Eklund_2012_RECURRENT PROCESSING AND THE CONSCIOUSNESS.pdf
    		However, we derive this conclusion from a more fundamental informational-related hypothesis indicating the more generalised principle behind it.

        % ---------------------------------------------------------------------------- %
        %                                Fail to meet 2                                %
        % ---------------------------------------------------------------------------- %
        \subsubsection*{Fail to meet the 2\lowercase{ed} condition}
        As mention above, information is level-dependent and can be virtually independent (closed) across different coarse-graining scales. If processes at some levels of a system are able to form high NTIC and become conscious, information at other levels still remains unconscious. The first implication of this argument is that processes at levels with high stochasticity are unable to form high NTIC and, therefore, unconscious. High stochasticity corrupts informational channel capacity and leads to low mutual information between past and future states of a process. In the neural system, the cellular level activities are highly noisy and are unable to reach high NTIC. Therefore, the information processed by the microscopic levels in the neural system are not conscious and we never can experience detail activities in the microscopic levels.

@@

% ============================================================================ %
%                        Comparison with other theories                        %
% ============================================================================ %
	\section{Comparison with other theories}\label{sec:Comparison with other theories}
	In this section, we compare our theory with other popular modern theories of consciousness.

        % ---------------------------------------------------------------------------- %
        %        Theories about multilevel views on consciousness and cognition        %
        % ---------------------------------------------------------------------------- %

@@

            It is important to note that the coarse-graining direction is not necessary aligned with \critical{Just saying anatomical is not enough. Need better expression} anatomical sensory hierarchy in the neural system. Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}. Due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels. In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system. We argue that previous data suggesting the neural correlates of consciousness between microscopic neural activities and conscious contents may be misled.

@@

		\subsection{Theories about multilevel views on consciousness and cognition}
		Previously, similar to our theory, several multilevel views on consciousness and cognition have been proposed. We shortly discuss two theories relevant to our current proposal.
            \subsubsection*{Level of Organisation \cite{wimsatt1994ontology}}
                As mentioned previously, the level of coarse-graining is different from the anatomical level.
                Pennartz focuses more on multimodal representation as the most important factor (See the discussion in \cite{pennartz2015brain}). Our proposal is inline with Pennartz's Neurorepresentational  theory (Neurorepresentationalism) \cite{pennartz2018consciousness,pennartz2015brain}. However, it’s crucial to note that our theory claims only the level of coarse-graining achieving NTIC matters to consciousness rather than the anatomical level of sensory hierarchy.

@@

			\subsubsection*{Pennartz's neurorepresentational theory (Neurorepresentationalism)}
			    Our theory shares some close concepts with Pennartz's Neurorepresentationalism \citep{pennartz2018consciousness,pennartz2015brain}. Similar to Neurorepresentationalism, our framework is also close to Marr's original distinction between the levels of analysis \citep{marr1982vision, pennartz2015brain, pennartz2018consciousness}. However, a fundamental difference between the two theories is that Neurorepresentationalism takes more functionalist point of view and suggests NCC should serve high-level world-modeling and makes a best guess about the interaction between the body and the environment. Neurorepresentationalism also suggests conscious experience is associated with integrated representation for multimodal and situational information. Out theory suggests that the association between the functions mentioned in Neurorepresentationalism is rooted in the more fundamental relationship between information and consciousness in which NTIC plays an important role.

        % ---------------------------------------------------------------------------- %
        %                             First-order theories                             %
        % ---------------------------------------------------------------------------- %
		\subsection{First-order theories}
            The first-order theories suggest that consciousness is determined by early sensory information or neural activities\needref{First-order theories}. The first-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
            First-order theories suggests that phenomenal consciousness is associated with fine-grained contents for the first-order processes. Different from the first-order theories, our theory suggests that, whether the early sensory activities show in the conscious content, it depends on information encoded in the early sensory areas is recruited in the NTIC process at the macroscopic level or not. As we mentioned in \ref{sec:Unconscious Processing}, if the sensory activities are only passively triggered by the environmental states, they are not able to form hign NTIC and remain unconscious. We predict that, if early sensory information or neural activities after coarse-graining take parts in the NTIC process, early sensory information or neural activities can contribute conscious content.

        % ---------------------------------------------------------------------------- %
        %                 Higher Order Thought theory of consciousness                 %
        % ---------------------------------------------------------------------------- %
		\subsection{Higher Order Thought theory of consciousness}
		    \ideaBox{Okay, I don't know how to deal with HOT now. I don't understand it at all}
		    In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations which represent agents as being in particular internal states \citep{lau2011empirical}. First-order processing needs to be observed or represented by a higher-order observer to become conscious.

		    Meta-cognition is also associated with many conscious cognitive function. However, we propose a new perspective and indicate that HOT may be a misunderstanding \critical{Very bad writing. I need to rewrite this part}.

		    This may be the result of neural coarse-graining. Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it.

		    Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation. It is true that the neural system does create  meta-representation to represent xxx\needref{Maybe come studies about confidence represenatation}. The higher-order representation may resemble coarse-grained variables. This may cause misidentify the entity which correlates conscious experience.

		    Moreover, the predictive information in NTIC is critical for other systems to build forward models for a wild range of tasks. Therefore, most of the high level cognition can utilise the state of informational closure. For example, mental planning needs a precise forward model to infer the environmental dynamics.

@@

        % multi NTIC problem
        Our theory is not complete yet. 
        To identify an NTIC individuals and their boundaries, we can adopt the algorithm for computing individuality developed by \cite{krakauer2014information}. This algorithm defines an individual starting from a small set of variables and repeatedly computes individuality after adding more variables into the system. If the measure of individuality increase, the algorithm considers the new variables as the part of the system, and vise verse. However, this algorithm does not consider coarse-grained processes in a system (see "Caveats and challenges"\cite[p. 13]{krakauer2014information}.

>>>>

        The two examples show that coding schemes through coarse-graining could provides a stochastic system, e.g. the neural system, to form more stable and deterministic macroscopic processes to encode and process information reliably. We argue that through coarse-graining the neural systems is able to form NTIC processes at macroscopic levels. Based on this argument, we proposes our theory of consciousness in the next section.

@@

        % ---------------------------------------------------------------------------- %
        %                            Unconscious Processing                            %
        % ---------------------------------------------------------------------------- %
        \subsection{Unconscious Processing}
            \ac{OurTheory} proposes that NTIC is sufficient for a process to be conscious. Based on the definition of NTIC, we highlights two scenarios which lead low NTIC so that a process is unconscious. We additionally highlight the level of coarse-graining.
            \ideaCallout{Need rewording}

            % ============================================================================ %
            %                                 Fail to be IC                                %
            % ============================================================================ %
            \subsubsection*{Fail to Form Informational Closure}
                A process is not informationally closed leads to low levels of NTIC (Eq.~\ref{eq:nticObjective2}) and results in low or no consciousness. In this case, the current states of a process are largely depends on its environment states (see Fig.~\ref{fig:reflexive}) but little influenced by its past states. Reflexive behaviours \citep{casali2013theoretically} can be considered a classical example in this scenario. \ac{OurTheory} naturally explains why reflexive behaviours always do not involve voluntary conscious controls and operate unconsciously.

             	% reflexive behaviour
        		\begin{figure}[H]
        			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
        			\caption{
        			    Reflexive behaviours happen between a process $Y$ and its environment $E$ which $Y$ interact with. The red nodes and arrows represent the major information flow in reflexive reactions. The internal state of the process $Y_t$ is largely dependent on the environment state $E_{t-1}$ but less on its past state $Y_{t-1}$. Therefore, the process $Y$ is not informational closed. In consequence, $Y$ is unable to form high NTIC and, therefore, to have high conscious levels.
        			    }
        			\label{fig:reflexive}
        		\end{figure}

        		The same principle can be applied to blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedure memory \citep{doyon2009contributions, ashby2010cortical} which are often considered as unconscious processes. Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements without having any conscious perception about visual stimuli. We argue that action outputs of blindsight can be directly guided by sensory inputs through stimulus-response maps. The neural circuits are not informationally closed and, therefore, unconscious. Similarly, for procedure memory, the state transitions of action controls largely depends on the concurrent environmental states. This prevents the internal processes of procedure memory from informational closure and being conscious.

                % In the neural system, this type of processes, for perception, shows the property that the perceptual processing mainly passively responds to the sensory inputs. For actions, this type of processes only produces "reflective-like" behaviours. Reflexive behaviours are commonly considered as automatic and non-conscious behavioural controls \citep{casali2013theoretically}\needref{More referene}. We argue that information carried by this type of processes is unconscious due to its failure of achieving high NTIC, i.e., the first condition.

                % The same principle can be applied to blindsight and procedure memory \needref{blindsight} which are often considered as unconscious processing. Blindsight patients are able to track objects, avoid obstacles, and make above chance-level judgements without having any conscious perception about visual stimuli. We believe that these behaviours can be guided by direct stimulus-response mappings ($S\rightarrow{}R$). However, the direct $S\rightarrow{}R$ mappings also lead to non-NTIC neural processes  and, therefore, are unconscious. Similarly, in the case of procedure memory, processes always rely on both the current environmental and system states to determine the next state of the processes\needref{Do I need ref??}. The information flow from the environment to the system is crucial to guide the state transition of procedural memory. Therefore, information processing of procedural memory also fails to form high NTIC and remain unconscious.

        %          This type of processing is similar to the model-free policy-based agents in the reinforcement learning framework. The agent learns a policy $\pi$ which directly maps sensor values $S$ to output action $A$.
        % 		\begin{equation}
        % 			\label{eq:PolicyBasedAgent}
        % 			\begin{aligned}
        % 			    \pi(A | S)=\operatorname{Pr}\left(A_{t}=a | S_{t}=s\right)
        % 			\end{aligned}
        % 		\end{equation}

                \ac{OurTheory} explains why the patients with visual apperceptive agnosia \citep{james2003ventral} can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}. The online information from the visual inputs can be used to perform  functional actions without complete conscious perception of the visual targets.

                % Our theory also explains why unconscious processes in this category often fail when a long delay periods is introduced in the tasks. Without self-predictive information in NTIC, the policies of motor outputs largely depends on the present environmental and sensory states implying that this type of processes often can only work online. With a long, sensory information is unable to guide the delayed motor outputs and leads to failure consequences.

        		\ideaCallout{Mayeb can put in theory part}
        		An implication from \ac{OurTheory} is that a pure feedforward network is incapable to be conscious due to a lack of any form of memory. Without memory, the network current states are entirely driven by network current inputs without any influence from its past states and, therefore, is incapable to be informationally closed. In contrast, a network with recurrent loops could keep information about its states. This forms an information channel between the past and the future states of the network and, thus, makes the network becomes capable of being informationally closed. This result coincides with theories of consciousness emphasising the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.

        % 		However, we derive this conclusion from a more fundamental informational-related hypothesis indicating the more generalised principle behind it.

            \subsubsection*{Encoded Information is Trivial}
                Encoded information in a process is trivial, i.e. no mutual information between the system states and its environment states $I(Y_{t+1};E_{t})$ (Eq.~\ref{eq:nticObjective2}), could also lead low NTIC. This process is considered to be unconscious due to the low level of NTIC. This implies an isolated process which is simply informationally closed to its environment is not enough to be conscious.

                This implies that \ac{OurTheory} provides a natural solution to the boundary problem of consciousness \citep{Raymont2006-RAYUOC}. Consider a NTIC process $Y$ and an isolated informationally closed process $\hat{Y}$ with trivial information. Adding $\hat{Y}$ to $Y$ can still keep informational closure, but, however, does not increase non-trivial information.

    			\begin{equation}
    			    \begin{aligned}
                        I(Y,\hat{Y};E) & = H(Y,\hat{Y}) - H(Y,\hat{Y}|E) \\
                                       & = H(Y) + H(\hat{Y}|Y) - (H(Y|E)+H(\hat{Y}|Y,E)) \\
                                       & = H(Y) + H(\hat{Y}) - (H(Y|E)+H(\hat{Y})) \\
                                       & = H(Y) - H(Y|E)\\
                                       & = I(Y;E)				
    				\end{aligned}
    			\end{equation}

                This indicates that isolated processes with trivial information do not contribute consciousness and should be outside the information boundary of the conscious processing. This result also implies that consciousness does not emerge from aggregating informationally closed processes with trivial information.

            % \ideaCallout{Should I say this?}
%             This implies that \ac{OurTheory} provides a natural solution to the boundary problem of consciousness \citep{Raymont2006-RAYUOC}. Consider a set of independent processes $Y=\{Y^1,...,Y^n\}$ with deterministic state transitions in a small universe. Each variable not only is informationally closed to other variables, they also share no mutual information.

% 			\begin{equation}
% 				\thickspace Y^i \bot Y^j, \quad \forall {i\neq j}
% 			\end{equation}

%             Now we randomly pick two variables and make group two variables s

%             , therefore, unconscious. Next, we can select a two of the variables and compute NTIC between this subset and other variables.

            \subsubsection*{Unsuitable Measurement scales }
                \ac{OurTheory} proposes that human conscious process rests on a certain scale which forms NTIC. This implies the spatial and temporal scales of the physiological measurements are critical in the experiments aiming to finding neural correlates of consciousness (NCC).

                % \subsubsection*{Fail t  o meet the 2\lowercase{ed} condition}
                As mention above, information is level-dependent and can be virtually independent (closed) across different coarse-graining scales. If processes at some levels of a system are able to form high NTIC and become conscious, information at other levels still remains unconscious. The first implication of this argument is that processes at levels with high stochasticity are unable to form high NTIC and, therefore, unconscious. High stochasticity corrupts informational channel capacity and leads to low mutual information between past and future states of a process. In the neural system, the cellular level activities are highly noisy and are unable to reach high NTIC. Therefore, the information processed by the microscopic levels in the neural system are not conscious and we never can experience detail activities in the microscopic levels.

@@

% ============================================================================ %
%                        Comparison with other theories                        %
% ============================================================================ %
	\section{Comparison with other Relevant Theories of Consciousness}\label{sec:Comparison with other theories}
	In this section, we \ac{OurTheory} with other relevant modern theories of consciousness.

        % ---------------------------------------------------------------------------- %
        %        Theories about multilevel views on consciousness and cognition        %
        % ---------------------------------------------------------------------------- %
        \subsection{Multilevel views on consciousness and cognition}
    		\ac{OurTheory} proposes that a conscious (NTIC) process only rest at a certain coarse-grained scale in the neural system. This suggests that the scales of coarse-graining is critical for searching for conscious processes. In previous research, a few multilevel views on consciousness have been (explicitly or implicitly) proposed. So far, to our knowledge, Pennartz's neurorepresentational theory (Neurorepresentationalism, \cite{pennartz2018consciousness,pennartz2015brain}) is the closest proposal in line with our multilevel view on consciousness. Similar to Neurorepresentationalism, the concept of levels \ac{OurTheory} is also relevant to Marr's level of analysis \citep{marr1982vision, pennartz2015brain, pennartz2018consciousness}. 
    		However, \ac{OurTheory} suggests that coarse-graining is necessary only when the microscopic processes are stochastic (e.g. the neural system). An NTIC process can be formed in a noise-free deterministic system without coarse-graining. According to \ac{OurTheory}, this NTIC process is sufficient to be conscious. 
    		Another fundamental difference between \ac{OurTheory} and Neurorepresentationalism is that Neurorepresentationalism takes functionalist perspective and suggests consciousness should serve high-level world-modelling and makes a best guess about the interaction between the body and the environment. 
    		%Neurorepresentationalism also suggests conscious experience is associated with integrated representation for multimodal and situational information.
    		However, \ac{OurTheory} is grounded by non-functional informational assumptions. Therefore, \ac{OurTheory} provides a more fundamental explanation for the scale problem of consciousness.

    		Another proposal based on multilevel views is the Intermediate Level Theory of Consciousness \citep[ILT]{prinz2007intermediate, jackendoff1987consciousness}. ILT proposes that conscious experience is only associated with representations at intermediate levels of the sensory processing hierarchy (e.g., the 2.5D representation in terms of visual processing) rather than lower (e.g. pixel) or higher (e.g. abstract ) levels of the hierarchy. 
    		Here, we want to make a clear clarification that the "level" in \ac{OurTheory} refers to the levels of coarse-graining instead of the "level" for anatomy or information processing. It is important to note that the coarse-graining direction is not necessary aligned with the levels of anatomy or the information processing hierarchy in the neural system . Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example

    		specific levels of representations in the hierarchy of sensory processing. ILT claims that consciousness only associates with the representation at intermediate levels (e.g., the 2.5D representation in terms of visual processing) rather than the ones at lower-level or higher-level.

    		One fundamental difference between ILT and our theory is the definitions of the level. In our theory, level is within the context of coarse-graining. However, ILT focuses more on the levels in terms of anatomical direction (see fig \ref{fig:hierarchy}). As mentioned previously, we emphasise that we doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies. This leads to an important difference that the level of coarse-graining exists virtually. However, the level of cortical representation should be referred to neural substrates. Finally, different from ILT which suggests that some neural substrates responsible for the 2.5D computation are conscious, we predict that once information carried by coarse-grained variables is involved in the NTIC process, brain areas, not exclusively within 2.5D representation, should  co-vary with conscious contents.

@@

        It is important to note that the coarse-graining direction is not necessary aligned with \critical{Just saying anatomical is not enough. Need better expression} anatomical sensory hierarchy in the neural system. Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example

        the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}. Due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels. In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system. We argue that previous data suggesting the neural correlates of consciousness between microscopic neural activities and conscious contents may be misled.

@@

                \subsubsection*{Level of Organisation \cite{wimsatt1994ontology}}
                    As mentioned previously, the level of coarse-graining is different from the anatomical level.
                    Pennartz focuses more on multimodal representation as the most important factor (See the discussion in \cite{pennartz2015brain}). Our proposal is inline with Pennartz's Neurorepresentational  theory (Neurorepresentationalism) \cite{pennartz2018consciousness,pennartz2015brain}. However, it’s crucial to note that our theory claims only the level of coarse-graining achieving NTIC matters to consciousness rather than the anatomical level of sensory hierarchy.

@@

        % ---------------------------------------------------------------------------- %
        %                             First-order theories                             %
        % ---------------------------------------------------------------------------- %
% 		\subsection{First-order theories}
            % The first-order theories suggest that consciousness is determined by early sensory information or neural activities\needref{First-order theories}. The first-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
            % First-order theories suggests that phenomenal consciousness is associated with fine-grained contents for the first-order processes. Different from the first-order theories, our theory suggests that, whether the early sensory activities show in the conscious content, it depends on information encoded in the early sensory areas is recruited in the NTIC process at the macroscopic level or not. As we mentioned in \ref{sec:Unconscious Processing}, if the sensory activities are only passively triggered by the environmental states, they are not able to form hign NTIC and remain unconscious. We predict that, if early sensory information or neural activities after coarse-graining take parts in the NTIC process, early sensory information or neural activities can contribute conscious content.

        % ---------------------------------------------------------------------------- %
        %                 Higher Order Thought theory of consciousness                 %
        % ---------------------------------------------------------------------------- %
% 		\subsection{Higher Order Thought theory of consciousness}
% 		    \ideaBox{Okay, I don't know how to deal with HOT now. I don't understand it at all}
% 		    In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations which represent agents as being in particular internal states \citep{lau2011empirical}. First-order processing needs to be observed or represented by a higher-order observer to become conscious.

% 		    Meta-cognition is also associated with many conscious cognitive function. However, we propose a new perspective and indicate that HOT may be a misunderstanding \critical{Very bad writing. I need to rewrite this part}.

% 		    This may be the result of neural coarse-graining. Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it.

% 		    Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation. It is true that the neural system does create  meta-representation to represent xxx\needref{Maybe come studies about confidence represenatation}. The higher-order representation may resemble coarse-grained variables. This may cause misidentify the entity which correlates conscious experience.

% 		    Moreover, the predictive information in NTIC is critical for other systems to build forward models for a wild range of tasks. Therefore, most of the high level cognition can utilise the state of informational closure. For example, mental planning needs a precise forward model to infer the environmental dynamics.

@@

        % Identity problem
        Our theory is not complete yet. 
        To identify an NTIC individuals and their boundaries, we can adopt the algorithm for computing individuality developed by \cite{krakauer2014information}. This algorithm defines an individual starting from a small set of variables and repeatedly computes individuality after adding more variables into the system. If the measure of individuality increase, the algorithm considers the new variables as the part of the system, and vise verse. However, this algorithm does not consider coarse-grained processes in a system (see "Caveats and challenges"\cite[p. 13]{krakauer2014information}.
